---
title: "R_markdown_shiny_example"
author: "Heather Welch"
date: "9/13/2017"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Trialing embedding rshiny widgets into rmarkdown documents using Savage's bycatch data
```{r,context="setup", include=FALSE}
library(shiny)
library(rmarkdown)
library(dplyr)
library(BayesFactorExtras)
library(knitr)

knitr::opts_chunk$set(echo = FALSE) ##beats me what this does

setDownloadURI = function(list, filename = stop("'filename' must be specified"), textHTML = "Click here to download the data.", fileext = "RData", envir = parent.frame()){
  require(base64enc,quietly = TRUE)
  divname = paste(sample(LETTERS),collapse="")
  tf = tempfile(pattern=filename, fileext = fileext)
  save(list = list, file = tf, envir = envir)
  filenameWithExt = paste(filename,fileext,sep=".")
  
  uri = dataURI(file = tf, mime = "application/octet-stream", encoding = "base64")
  cat("<a style='text-decoration: none' id='",divname,"'></a>
    <script>
    var a = document.createElement('a');
    var div = document.getElementById('",divname,"');
    div.appendChild(a);
    a.setAttribute('href', '",uri,"');
    a.innerHTML = '",textHTML,"' + ' (",filenameWithExt,")';
    if (typeof a.download != 'undefined') {
      a.setAttribute('download', '",filenameWithExt,"');
    }else{
      a.setAttribute('onclick', 'confirm(\"Your browser does not support the download HTML5 attribute. You must rename the file to ",filenameWithExt," after downloading it (or use Chrome/Firefox/Opera). \")');
    }
    </script>",
    sep="")
}

# load data

```

```{r results='asis',echo=FALSE,message=FALSE}
# setDownloadURI("dataset", filename = "bycatch")
knitr::include_app("https://heatherwelch.shinyapps.io/rshinyapp_historical/",height="600px")

```


```{r eruptions, echo=FALSE}
# library(shiny)
# inputPanel(
#   selectInput("n_breaks", label = "Number of bins:",
#               choices = c(10, 20, 35, 50), selected = 20),
#   
#   sliderInput("bw_adjust", label = "Bandwidth adjustment:",
#               min = 0.2, max = 2, value = 1, step = 0.2)
# )
# 
# renderPlot({
#   hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
#        xlab = "Duration (minutes)", main = "Geyser eruption duration")
#   
#   dens <- density(faithful$eruptions, adjust = input$bw_adjust)
#   lines(dens, col = "blue")
# })
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
# shinyAppDir(
#   system.file("examples/06_tabsets", package = "shiny"),
#   options = list(
#     width = "100%", height = 550
#   )
# )
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



