---
title: "Building an interactive histogram in shiny"
author: "Heather Welch"
date: "9/14/2017"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Creating a **shiny app:** best practices.

1. create a new dirctory: "app name".
2. create a new directory: "app name"/data.
3. place any necessary data in "app name"/data.
4. create new r script "app name"/app.R (shiny apps need to be named this)

Creating a **shiny app:** code structure.

1. load all your libraries.
2. load all your data.
3. UI(): User Interface. This code block defines app layout and inputs.
4. Server(): This code block defines what to do with inputs. This is the workhorse of your app.
5. Run the application

Lets take a look.

```{r,message=FALSE}
# 1. load all your libraries.
library(shiny)
library(rsconnect)
```

**Description:**

the **shiny** package loads all the interactive tools, the **rsconnect** package allows apps to be published

```{r}
# 2. load all your data.
dataset=read.csv("data/bycatch_data.csv")
```

**Description:**

Your app will reference all pathways to itself (i.e. the parent folder), therefor pathways can be defined in relation. Always nest items called by your app within the parent folder
```{r}
# 3. UI{}: User Interface. This code block defines app layout and inputs.
ui <-shinyUI(fluidPage(
  selectInput(inputId = "column",
              label = "DataFrame column",
              choices = c("TOTAL.FISHERY.BYCATCH","TOTAL.FISHERY.LANDINGS","FISHERY.BYCATCH.RATIO")),
  
  plotOutput(outputId = "main_plot")
))
```

**Description:**

**fluidpage()** turns your app layout into a grid of rows and columns, so that you can define where in the grid each widget (shiny element) is placed.  
**selectInput()** is the call for an interactive input box, where the end user can make a selection from pre-defined choices.  
**inputId** is an id that will be used to call up the end user's selection in the server() section.  
**choices** defines the pre-defined choices from which the user can select. These are three columns in the bycatch dataset.  
**plotOutput** creates a place holder for our desired output (in this case a plot), which we will build upon in the server() section.  

```{r}
# 4. Server(): This code block defines what to do with inputs. This is the workhorse of your app.
server <- shinyServer(function(input, output) {
  
  output$main_plot <- renderPlot({
    col=input$column
    index=as.numeric(grep(col,colnames(dataset)))
    hist(dataset[[index]],
         xlab = col,
         main = paste0("Histogram of ",col))
  })
  
})
```

**Description:**

**output"dollar sign"main_plot** references the place holder output we built in the UI() section  
**renderPlot** creates a reactive plot that's responsive to end user selection  
**input$column** grabs the id we created with inputId in the UI() section  
**hist()** is regular r code for building a histogram. In this case the histogram is reactive to the end user's selection (i.e. the selected dataframe column)  
```{r}
# 5. Run the application
shinyApp(ui = ui, server = server)
```



metadata  
This app was created within an rmarkdown document using runtime: shiny to allow for interactive components  
The completed .Rmd was published to shinyapps.io using rsconnect::deployApp  
**deploying your app**
1. create a shinapps.io account  
2. click on the tokens tab, click "show"
3. copy and run authorization in r, e.g.  
rsconnect::setAccountInfo(name='heatherwelch', token='B2988C7352F4325DBE32245C056421D0', secret='DjQTn0FsvWCwu6bxLCn236pR7hdf82haJUXu6Tyg')  
4. setwd to app dir, run rsconnect::deployApp()