---
title: "Introduction to rshiny"
author: "Heather Welch"
date: "9/14/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Creating a **shiny app:** best practices.

1. create a new dirctory: "app name".
2. create a new directory: "app name"/data.
3. place any necessary data in "app name"/data.
4. create new r script "app name"/app.R (shiny apps need to be named this)

Creating a **shiny app:** code structure.

1. load all your libraries.
2. load all your data.
3. UI(): User Interface. This code block defines app layout and inputs.
4. Server(): This code block defines what to do with inputs. This is the workhorse of your app.

Lets take a look.
```{r}
# 1. load all your libraries.
library(shiny)

# 2. load all your data.
dataset=read.csv(data/bycatch_data.csv)

# 3. UI{}: User Interface. This code block defines app layout and inputs.
ui <-shinyUI(
  
)

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
